---
title       : 1994 Belgian Wage Analysis App
subtitle    : 
author      : Martin Richard
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose of App

* Use economic data from the Ecdat package to see difference between different experience levels and education of Belgian workers
* Plots data and allows user to view data points of specific entries
* Reports mean of the subset
* App is available to use on [shinyapps](https://mjrichard.shinyapps.io/AppBelgiumWage)
* Convenient visualization of the data

---  

## Interactivity

* Multiple Options are given for which subset of the data to observe
* Look at wages for
    * The entire data set
    * A specific amount of experience across all education levels
    * A specific amount of education across all experience levels
    * A specific education and experience level
        * Will produce some empty data sets for some selections

---

## About the dataset

* From the Ecdat package (available from CRAN)
* Variables are
    * wage: Gross hourly wage in euro
    * educ: Education level on a scale from 1 to 5
    * exper: years of experience
    * sex: values not actually included in dataset

        
```{r, message=FALSE}
library(Ecdat)
data(Bwages)
str(Bwages)
```

---

## Sample plot of the entire dataset

```{r, echo=FALSE}
library(ggplot2)
```
The mean of the data is 
```{r}
mean(Bwages$wage)
```

```{r, fig.height=4, fig.width=6}
qplot(exper, wage, data=Bwages,xlim=c(0,47),ylim=c(0,50), col=educ)

```




